The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Update major merger citations

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution as a
result of \textit{Gaia} Data Release 2 (DR2).  Recent major discoveries
include the remnants of a major merger \citep{2018ApJ...860L..11K,
2018Natur.563...85H, 2018arXiv180704290L, 2019MNRAS.482.3426M}, a phase-space
``spiral'' in the solar neighborhood \citep{2018Natur.561..360A} possibly
indicating local substructure infall \citep{2018MNRAS.481.1501B,
2018arXiv180800451L}, and a gap
suggestive of perturbation by a dark matter subtructure in the tidal stream
GD1 \citep{2018ApJ...863L..20P, 2018arXiv181103631B}. These discoveries all
indicate that the Milky Way's stellar distribution, which demonstrably departs
significantly from axisymmetry, is undergoing phase mixing and dynamical
interactions across a range of spatial and temporal scales.

>>>>

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution as a
result of \textit{Gaia} Data Release 2 (DR2).  Recent major discoveries
include the affirmation of remnants of a major merger \citep{2018ApJ...860L..11K, 2018MNRAS.478..611B, 2018Natur.563...85H, 2019MNRAS.486..378L, 2019MNRAS.482.3426M} hinted at in pre-\textit{Gaia} work \citep[e.g.][]{2005MNRAS.359...93M, 2011MNRAS.412.1203N}, a phase-space
``spiral'' in the solar neighborhood \citep{2018Natur.561..360A} possibly
indicating local substructure infall \citep{2018MNRAS.481.1501B,
2018arXiv180800451L}, and a gap
suggestive of perturbation by a dark matter subtructure in the tidal stream
GD1 \citep{2018ApJ...863L..20P, 2018arXiv181103631B}. These discoveries all
indicate that the Milky Way's stellar distribution, which demonstrably departs
significantly from axisymmetry, is undergoing phase mixing and dynamical
interactions across a range of spatial and temporal scales.
